### 2025-01-31 Paper/CAGEO_LaTeXTemplate-main/main_document.tex
rgd

\title [mode = title]{A Fast Method for Detecting Rock Blocks and Computing Volumes and 3D Surface Areas}

@@

please find the enclosed manuscript "A Fast Method for Detecting Rock Blocks and Computing Volumes and 3D Surface Areas" which i am submitting for exclusive consideration for publication in Computers \& Geosciences. I confirm that the submission follows all the requirements and includes all the items of the submission checklist.  
\newline

@@

Name of the code/library

Contact: e-mail and phone number

Hardware requirements: ...

Program language: ...

Software required: ...

Program size: ...

The source codes are available for downloading at the link:
https://github.com/ . . . .

>>>>

\title [mode = title]{A Fast Method for Detecting Rock Blocks and Calculating Volumes and 3D Surface Areas}

@@

please find the enclosed manuscript "A Fast Method for Detecting Rock Blocks and Calculating Volumes and 3D Surface Areas" which i am submitting for exclusive consideration for publication in Computers \& Geosciences. I confirm that the submission follows all the requirements and includes all the items of the submission checklist.  
\newline

@@

Name of the code: rock\_segmentation

Contact: ali.polat@afad.gov.tr

Hardware requirements:

Program language: Python

Software required: Python v3.9

Program size: 35.7 KB

The source codes are available for downloading at the link:
https://github.com/apolat2018/rock\_segmentation
